Course Project 1
=================
##Load and process the data
- Step 1a: Load the packages
```{r,results="hide"}
library(dplyr)
library(lubridate)
library(ggplot2)
```
- Step 1b: Load the data
```{r}
df <- read.csv("activity.csv",header=TRUE)
```
- Step 2: Clean the data
```{r}
df$date <- ymd(df$date)
```
##What is the mean total number of steps taken per day?

- Step 1: Calculate the total number of steps taken per day

```{r}
data <- df%>%
    filter(!is.na(steps))%>%
    group_by(date)%>%
    summarize(steps=sum(steps))%>%
    print
```

- Step 2: Plot a histogram of the total number of steps taken each day

```{r}
hist(data$steps)
```

- Step 3: Calculate the mean and media

```{r}
mean<-mean(data$steps,na.rm=TRUE)
mean
median<-median(data$steps,na.rm=TRUE)
median
```

##What is the average daily activity pattern?
 
- Step 1: Time series plot of the 5-minute interval and average number of steps taken across all days

```{r}
timeseries <- df%>%
    filter(!is.na(steps))%>%
    group_by(interval)%>%
    summarize(steps=mean(steps))
plot(x=timeseries$interval,y=timeseries$steps,type="l")
```

- Step 2: What is the maximum interval?
```{r}
maximum<-timeseries[which(timeseries$steps==max(timeseries$steps)),]
maximum$interval
```

##Finding missing values

- Step 1: Report the total number of missing values in the dataset

```{r}
#na_set <- is.na(df$steps)
#count(na_set)
```

- Step 2&3: Fill in missing values & create new dataset with the values filled in
```{r}
new_df <- df
na_set <- is.na(new_df$steps)
averageSteps <- tapply(new_df$steps,new_df$interval,mean,na.rm=TRUE,simplify=TRUE)
new_df$steps[na_set]<-averageSteps[as.character(new_df$interval[na_set])]
```

- Step 4: Count the number of steps
```{r}
newNew_data <- new_df%>%
    group_by(date)%>%
    summarize(steps=sum(steps))%>%
    print
```

- Step 5: Create a histogram and calculate the mean and median of steps for the new dataset

```{r}
hist(newNew_data$steps)
new_mean<-mean(newNew_data$steps)
new_mean
new_median<-median(newNew_data$steps)
new_median
```

##Are there differences in activity patterns between weekdays and weekends?

- Step 1: Create a factor variable for weekday/weekend

```{r}
new_df <- mutate(new_df, typeday = ifelse(weekdays(new_df$date) == "Saturday" | weekdays(new_df$date) == "Sunday", "weekend", "weekday"))
new_df$typeday <- as.factor(new_df$typeday)
head(new_df)
```

- Step 2: Plot the difference between weekday and weekend 5-minute interval averages

```{r}
fivemin<-new_df%>%
    group_by(interval,typeday)%>%
    summarize(steps=mean(steps))

s <- ggplot(fivemin, aes(x=interval, y=steps, color = typeday)) +
  geom_line() +
  facet_wrap(~typeday, ncol = 1, nrow=2)
print(s)
```
